WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-22 article/Article.tex
fix typo
darcs-hash:20060321095655-2fc9d-6e1d82c017100ddddd4639421532ad9c0dd5076a.gz
add a note about article status
darcs-hash:20060322102716-2fc9d-e829b2f6f0a9b1af82b4f51f304765422fde9a20.gz

Currently, WrapITK only supports Python properly; Java and Tcl libraries build
correctly but the Java and Tcl support classes for loading these libraries needs
some updating.

It have been tested on Mandriva Linux, and MacOS X.

@@

Project should always be built outside the source directory, in a \veb$build$
directory for example.

>>>>

Currently, WrapITK have been tested on Mandriva Linux, and MacOS X, and only
supports Python properly; Java and Tcl libraries build
correctly but the Java and Tcl support classes for loading these libraries needs
some updating.

The article you're reading is not as nice and complete than what we would have
done, but it seems important to us to release our work and to get feedbacks
as soon as possible. The article will continue to evolve with WrapITK.

@@

Project should always be built outside the source directory, in a \verb$build$
directory for example.
